### 2022-06-30 letter.tex
Create letter.tex

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage[sfdefault]{noto}

% margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
%\date{yyyy-mm-dd}
\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
\raggedbottom

\begin{document}

\begin{letter}{
theirname \\
theirtitle \\
theircompany \\
theirstreet1 \\
theirstreet2 \\
theircity~ theirstate~~ theirzip
}

myname \\
mytitle \\
mystreet1 \\
mystreet2 \\
mycity~ mystate~~ myzip \\
phone \\
email
% \vfill

\signature{myname}

% letter content
\opening{subject \\ \\ Dear Sir or Madam:}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\closing{Regards,}

\encl{document1, document2, document3}

\end{letter}
\end{document}

### 2022-06-30 letter.tex
Update content

@@
-\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
+\documentclass[11pt]{letter}
 \usepackage[sfdefault]{noto}
-
-% margins
-\topmargin=-1in % Moves the top of the document 1 inch above the default
-\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
-\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
-\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
-%\date{yyyy-mm-dd}
-\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
+\topmargin=-1in
+\textheight=10in
+\oddsidemargin=-10pt
+\textwidth=6.5in
+\date{yyyy-mm-dd}
+\let\raggedleft\raggedright
 \raggedbottom
+\signature{myname}
 
 \begin{document}
-
 \begin{letter}{
@@
 theirstreet2 \\
-theircity~ theirstate~~ theirzip
+theircity\ \ theirstate\ \ \ \ theirzip
 }
@@
 email
-% \vfill
 
-\signature{myname}
+\opening{subject \\ \\ Dear theirname:}
 
-% letter content
-\opening{subject \\ \\ Dear Sir or Madam:}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
@@
 \closing{Regards,}
-
 \encl{document1, document2, document3}
-
 \end{letter}

### 2022-07-04 letter.tex
Update content

@@
 \signature{myname}
-
 \begin{document}
@@
 theirstreet2 \\
-theircity\ \ theirstate\ \ \ \ theirzip
+theircity\ \ theirstate\ \ \ \ theirzip \\
+their phone \\
+their email
 }
@@
 mycity~ mystate~~ myzip \\
-phone \\
-email
+myphone \\
+myemail
 

### 2022-07-06 article.tex
Create article.tex

% This is a template for documentclass{article}.

% must always be first line of a .tex document
\documentclass[12pt, letterpaper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[sfdefault]{noto}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-1in}
\setlength{\oddsidemargin}{.25in}
\setlength{\evensidemargin}{.25in}

% this package has better control over the date format
\usepackage{datetime2}

\usepackage{graphicx}
\graphicspath{{fot/}}
\usepackage[export]{adjustbox}
\usepackage[singlelinecheck=false,justification=justified]{caption}
\usepackage{titling}
\setlength{\droptitle}{-8pt}
\pretitle{\begin{flushleft}\LARGE\bfseries}
\posttitle{\par\end{flushleft}}
\preauthor{\begin{flushleft}\LARGE}
\postauthor{\end{flushleft}}
\predate{\begin{flushleft}}
\postdate{\end{flushleft}}
\date{\today}
\title{article title}
\author{article author}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\raggedbottom
\renewenvironment{abstract}{\par\noindent\textbf{\abstractname}\par}

\begin{document}
\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}

\section{Introduction}
\label{sec:introduction}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{Prior research}
\label{sec:results}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{Results}
\label{sec:results}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{Work in progress}
\label{sec:results}

\begin{figure}[h]
\includegraphics[width=\textwidth, inner]{matplotlib_anatomy_of_a_figure}
\caption{Anatomy of a matplotlib figure}
\end{figure}

Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

tables

equastions

matrices

lists

\end{document}

### 2022-07-06 article.tex
Add content

@@
 % This is a template for documentclass{article}.
+% See https://ctan.org/ for available packages and documentation.
 
@@
 
+% this package has better control over "floats"
+\usepackage{float}
+
 \usepackage{graphicx}
@@
 \usepackage[singlelinecheck=false,justification=justified]{caption}
+
+% this package has better control of title, author elements
 \usepackage{titling}
@@
 
-\begin{figure}[h]
-\includegraphics[width=\textwidth, inner]{matplotlib_anatomy_of_a_figure}
+\subsection{Graphics}
+\label{sec:graphics}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+% H means "here definitely" to place the figure
+\begin{figure}[H]
+% \includegraphics[width=\textwidth, inner]{matplotlib_anatomy_of_a_figure}
+\includegraphics[width=3in, inner]{matplotlib_anatomy_of_a_figure}
 \caption{Anatomy of a matplotlib figure}
@@
 
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\subsection{Inline mathematics}
+\label{sec:inline_mathematics}
+Examples of inline mathematics $\frac{a}{b}$, followed by text and another inline equation $\lim_{x\to 0}\frac{\sin x}{x}$=1 and more text $\sum_{k=0}^\infty \frac{1}{2^k}=2$ and finally much more text to cover many lines of a paragraph.
+
+\subsection{Separate mathematics}
+\label{sec:separate_mathematics}
+Examples of mathematics on their own lines.
+
+\subsection{Still to do}
+\label{sec:still_to_do}
+
 Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.
 
+\subsubsection{Even more to do}
+\label{sec:even_more_to_do}
 tables

### 2022-07-07 article.tex
Change double quotes to single, add inline equation
Add display-style mathematics, fix labels

@@
 
-% must always be first line of a .tex document
-\documentclass[12pt, letterpaper, twoside]{article}
+% must always be first line of a <path.tex> document
+\documentclass[10pt, letterpaper, twoside]{article}
 \usepackage[utf8]{inputenc}
@@
 
-% this package has better control over "floats"
+% this package has better control over 'floats'
 \usepackage{float}
@@
 
+% very useful for mathematics
+\usepackage{amsmath, amsthm, amssymb}
+
 \begin{document}
@@
 \section{Prior research}
-\label{sec:results}
+\label{sec:prior_research}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 \section{Work in progress}
-\label{sec:results}
+\label{sec:work_in_progress}
 
@@
 
-% H means "here definitely" to place the figure
+% H means 'here definitely' to place the figure
 \begin{figure}[H]
@@
 
-\subsection{Separate mathematics}
-\label{sec:separate_mathematics}
+\subsection{Display-style mathematics}
+\label{sec:display_style_mathematics}
 Examples of mathematics on their own lines.
+All equations are flush-left to the page unless multilines, and thus aligned on a symbol with the longest equation flush-left.
+The equations numbers are flush-right.
+
+\begin{flalign}
+    \text{measured observation} = \text{true value} + \text{measurement system error}&&
+\end{flalign}
+
+\begin{flalign}
+    \text{ICC} = \frac{\text{variance of the product values}}{\text{variance of the product observations}}&&
+\end{flalign}
+
+\begin{flalign}
+    \overline{X}  \pm \text{CI} & = \frac{\sum\limits_{i=1}^{n} X_i}{n} \pm t_{1- \alpha / 2 \, \text{,} \, n-1} \times \frac{s}{\sqrt{n}}&& \\
+    \text{distance to target} & = \text{specification target} - \text{location statistic} = T - \overline{X}&&
+\end{flalign}
+
+\begin{flalign}
+    s \pm \text{CI} & = \sqrt{\frac{\sum\limits_{i=1}^{n} \left(X_i - \overline{X}\right)^2}{n - 1}} \pm \left(\sqrt{\frac{(n - 1)\,s^{2}}{\chi_{\alpha / 2}^2}},\sqrt{\frac{(n - 1)\,s^{2}}{\chi_{1 - {\alpha / 2}}^2}}\right)&& \\
+    \text{distance to nearest specification} & = \frac{\text{nearest specification} - \text{location statistic}}{\text{dispersion statistic}}&& \\
+                                             & = \frac{\text{min}\,(\overline{X} - \text{LSL}\,, \text{USL} - \overline{X})}{s}&&
+\end{flalign}
+
+The confidence intervals are:
+
+\begin{flalign}
+    \text{Lower bound} = \hat{P}_{pk} - z_{1 - \alpha / 2} \sqrt{\frac{1}{\left(\frac{\text{toler}}{2}\right)^2 n} + \frac{\left(\hat{P}_{pk}\right)^2}{2 \nu}}&&
+\end{flalign}
+
+\begin{flalign}
+    \text{Upper bound} = \hat{P}_{pk} + z_{1- \alpha / 2} \sqrt{\frac{1}{\left(\frac{\text{toler}}{2}\right)^2 n} + \frac{\left(\hat{P}_{pk}\right)^2}{2 \nu}}&&
+\end{flalign}
+
+where:
+
+\begin{flalign*}
+    n                           & = \text{the number of observations in the sample}&& \\
+    \nu                         & = \text{the degrees of freedom $= n - 1$}&& \\
+    \chi_{\alpha \text{,}\nu}^2 & = \text{the $\alpha$ percentile of the chi-square distribution with $\nu$ degrees of freedom}&& \\
+    \text{toler}                & = \text{multiplier of the standard deviation tolerance (Minitab\textregistered\ uses 6 as the default value)}&& \\
+    z_{1 - \alpha / 2}          & = \text{the $1 - \alpha / 2$ percentile of the standard normal distribution}&& \\
+\end{flalign*}
 
@@
 
-equastions
-
 matrices

### 2022-07-07 article.tex
Add table of contents
Add list of equations
Add list of tables

@@
 
+% to create a list of equations
+\usepackage{tocloft}
+\setlength{\cfttabindent}{0in}
+\setlength{\cftfigindent}{0in}
+
+% used to create tables
+\usepackage{booktabs}
+
 \begin{document}
@@
 
+% create a list of equations command
+\newcommand{\listequationsname}{List of Equations}
+\newlistof{myequations}{equ}{\listequationsname}
+\newcommand{\myequations}[1]{%
+\addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}
+\renewcommand{\cftequtitlefont}{\normalfont\Large\bfseries}
+
+\tableofcontents
+
+\newpage
 \section{Introduction}
@@
 
-\subsection{Graphics}
+\section{Graphics}
 \label{sec:graphics}
@@
 \begin{figure}[H]
+\label{fig:anatomy_of_a_matplotlib_figure}
 % \includegraphics[width=\textwidth, inner]{matplotlib_anatomy_of_a_figure}
-\includegraphics[width=3in, inner]{matplotlib_anatomy_of_a_figure}
+\includegraphics[width=3in, left]{matplotlib_anatomy_of_a_figure}
 \caption{Anatomy of a matplotlib figure}
@@
 
+\section{Tables}
+\label{sec:tables}
+
+\begin{table}[H]
+\begin{flushleft}
+\begin{tabular}{lcccccc}
+\toprule
+& I &  II & III & IV & V & VI \\
+\midrule
+Vandali     & 123 & 456 & 678 & 321 & 644 & 768  \\
+Visigothorum & 021 & 229 & 678 & 123 & 456 & 678 \\
+\bottomrule
+\end{tabular}
+\label{tab:visigothi_cum_romanis}
+\caption{Visigothi cum Romanis}
+\end{flushleft}
+\end{table}
+
+\begin{table}[H]
+\begin{flushleft}
+\begin{tabular}{ccc}
+\toprule
+$A$ & $B$ & $ A \land B$ \\
+\midrule
+T & T & T \\
+T & F & F \\
+F & T & F \\
+F & F & F \\
+\bottomrule
+\end{tabular}
+\label{tab:boolean_truth_table}
+\caption{Boolean truth table}
+\end{flushleft}
+\end{table}
+
+\section{Mathematics}
+\label{sec:mathematics}
+
 \subsection{Inline mathematics}
-\label{sec:inline_mathematics}
+\label{sec:inline_mathematics}`
 Examples of inline mathematics $\frac{a}{b}$, followed by text and another inline equation $\lim_{x\to 0}\frac{\sin x}{x}$=1 and more text $\sum_{k=0}^\infty \frac{1}{2^k}=2$ and finally much more text to cover many lines of a paragraph.
@@
 \end{flalign}
+\myequations{Measured observation}
 
@@
 \end{flalign}
+\myequations{Intraclass correlation coefficient}
 
 \begin{flalign}
-    \overline{X}  \pm \text{CI} & = \frac{\sum\limits_{i=1}^{n} X_i}{n} \pm t_{1- \alpha / 2 \, \text{,} \, n-1} \times \frac{s}{\sqrt{n}}&& \\
+    \overline{X}  \pm \text{CI} & = \frac{\sum\limits_{i=1}^{n} X_i}{n} \pm t_{1- \alpha / 2 \, \text{,} \, n-1} \times \frac{s}{\sqrt{n}}&&
+\end{flalign}
+\myequations{Average $\pm$ confidence interval}
+
+\begin{flalign}
     \text{distance to target} & = \text{specification target} - \text{location statistic} = T - \overline{X}&&
 \end{flalign}
+\myequations{Distance to target}
 
 \begin{flalign}
-    s \pm \text{CI} & = \sqrt{\frac{\sum\limits_{i=1}^{n} \left(X_i - \overline{X}\right)^2}{n - 1}} \pm \left(\sqrt{\frac{(n - 1)\,s^{2}}{\chi_{\alpha / 2}^2}},\sqrt{\frac{(n - 1)\,s^{2}}{\chi_{1 - {\alpha / 2}}^2}}\right)&& \\
+    s \pm \text{CI} & = \sqrt{\frac{\sum\limits_{i=1}^{n} \left(X_i - \overline{X}\right)^2}{n - 1}} \pm \left(\sqrt{\frac{(n - 1)\,s^{2}}{\chi_{\alpha / 2}^2}},\sqrt{\frac{(n - 1)\,s^{2}}{\chi_{1 - {\alpha / 2}}^2}}\right)&&
+\end{flalign}
+\myequations{Standard deviation $\pm$ confidence interval}
+
+\begin{flalign}
     \text{distance to nearest specification} & = \frac{\text{nearest specification} - \text{location statistic}}{\text{dispersion statistic}}&& \\
@@
 \end{flalign}
+\myequations{Distance to nearest specification}
 
@@
 \end{flalign}
+\myequations{$\hat{P}_{pk}$ lower bound}
 
@@
 \end{flalign}
+\myequations{$\hat{P}_{pk}$ upper bound}
 
@@
 
-\subsection{Still to do}
+\section{Still to do}
 \label{sec:still_to_do}
 
+\subsection{Almost done}
+\label{sec:even_more_to_do}
 Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.
 
-\subsubsection{Even more to do}
+\subsubsection{Not started}
 \label{sec:even_more_to_do}
-tables
-
 matrices
@@
 
+\newpage
+\listoffigures
+
+\newpage
+\listoftables
+
+\newpage
+\listofmyequations
+
 \end{document}

### 2022-07-08 article.tex
Clean up preamble
Add acknowledgement
Add supporting information
Add citations, bibliography
Add bold, italics, underline

@@
 \setlength{\evensidemargin}{.25in}
-
-% this package has better control over the date format
-\usepackage{datetime2}
-
-% this package has better control over 'floats'
-\usepackage{float}
-
-\usepackage{graphicx}
-\graphicspath{{fot/}}
-\usepackage[export]{adjustbox}
-\usepackage[singlelinecheck=false,justification=justified]{caption}
 
@@
 
+% this package has better control over the date format
+\usepackage{datetime2}
+
+% this package has better control over 'floats'
+\usepackage{float}
+
+% this package has better control over images
+\usepackage{graphicx}
+\graphicspath{{fot/}}
+\usepackage[export]{adjustbox}
+\usepackage[singlelinecheck=false,justification=justified]{caption}
+
 % very useful for mathematics
@@
 \usepackage{booktabs}
+
+% set references indent
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
 \section{Results}
@@
 
-\section{Work in progress}
-\label{sec:work_in_progress}
+\section{Bold, italics, and underline}
+\label{sec:bold_italics_underline}
+Bold text is done with \textbackslash{textbf\{\textless text \textgreater\}} such as \textbf{bolded text}.
 
+Italics text is done with \textbackslash{textit\{\textless text \textgreater\}} such as \textit{italics text}.
+
+Underline text is done with \textbackslash{underline\{\textless text \textgreater\}} such as \underline{italics text}.
+
+Bold and italics text is done with \textbackslash{textbf\{\textbackslash{textit\{\textless text \textgreater\}\}} such as \textbf{\textit{bolded text}}.
+
+Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.
+
+\newpage
 \section{Graphics}
@@
 
+\newpage
 \section{Tables}
@@
 
+\newpage
 \section{Mathematics}
@@
 
+\newpage
+\section{Citations}
+\label{sec:citations}
+The formatting of the bibliography is not quite what I wish. I will explore bibtex for this. For now, here is how to site articles, books, and online references.
+
+Blah blah \cite{JD} and blah blah \cite{JS} and blah blah \cite{JT}.
+
 \section{Still to do}
 \label{sec:still_to_do}
-
-\subsection{Almost done}
-\label{sec:even_more_to_do}
-Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.
 
@@
 matrices
-
-lists
 
@@
 
+\section{Acknowledgement}
+\label{sec:acknowledgement}
+
+The author wishes to thank ...
+
+\section{Supporting information}
+\label{sec:supporting_information}
+
+Add files, data, and other supporting information, and where it can be obtained.
+
+\begin{thebibliography}{99}
+\bibitem{JD} Doe, John. 2000. Title of book.
+\bibitem{JS} Smith, John. 2013. \textit{Title of article}.
+\bibitem{JT} Thomas, John. 2022. \textit{Online reference}.
+\end{thebibliography}
+
 \end{document}

### 2022-07-08 article.tex
Add lists
Add definitions

@@
 
+% useful for definitions, theorems, corollaries, etc.
+\theoremstyle{myenv}
+\theoremstyle{mytheorem}
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{axiom}[theorem]{Axiom}
+\theoremstyle{mydefinition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{exercise}[theorem]{Exercise}
+\newtheorem{question}[theorem]{Question}
+\newtheorem{problem}[theorem]{Problem}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{remark}[theorem]{Remark}
+
+% set no indent for lists
+\usepackage{enumitem}
+\setlist[itemize]{leftmargin=*}
+\setlist[enumerate]{leftmargin=*}
+
 \begin{document}
@@
 \renewcommand{\cftequtitlefont}{\normalfont\Large\bfseries}
+
+% create a list of definitions command
+\newcommand{\listdefinitionsname}{List of Definitions}
+\newlistof{mydefinitions}{def}{\listdefinitionsname}
+\newcommand{\mydefinitions}[1]{%
+\addcontentsline{def}{mydefinitions}{\protect\numberline{\thedefinition}#1}\par}
+\renewcommand{\cftdeftitlefont}{\normalfont\Large\bfseries}
 
@@
 
+\newpage
 \section{Bold, italics, and underline}
@@
 Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.
+
+\section{Lists}
+Unordered list
+\begin{itemize}
+    \item Illinois
+        \begin{itemize}
+            \item Chicago
+            \item Naperville
+        \end{itemize}
+    \item Kentucky
+        \begin{itemize}
+            \item Lexington
+            \item Louisville
+        \end{itemize}
+\end{itemize}
+
+Ordered list
+\begin{enumerate}
+    \item Cat
+        \begin{enumerate}
+            \item Persian
+            \item Siamese
+        \end{enumerate}
+    \item Dog
+        \begin{enumerate}
+            \item Aussiedoodle
+            \item Newfoundland
+        \end{enumerate}
+\end{enumerate}
 
@@
 
+\section{Definitions}
+\label{sec:definitions}
+
+\begin{definition}[Definition of limit]
+\label{def:limit}
+Let $f$ be a function defined on an open interval containing $x=a$, but perhaps not at $x=a$.
+We say $\displaystyle\lim_{x\to a}f(x)=L$ if for any $\epsilon>0$ there exists $\delta>0$ such that $|f(x)-L|<\epsilon$ whenever $0<|x-a|<\delta$.
+\end{definition}
+\mydefinitions{Definition of limit}
+
+\begin{definition}
+\label{def:derivative}
+The \textit{derivative} of $f$ is defined to be $\displaystyle f^\prime(x)=\lim_{h\to 0}\frac{f(x+h)-f(x)}{h}$, if this limit exists.
+\end{definition}
+\mydefinitions{Derivative of f}
+
+\section{Theorems}
+\label{sec:theorems}
+
+\begin{theorem}[Fundamental Theorem of Calculus]
+\label{thm:ftc}
+If $f$ is continuous on the interval $[a,b]$, then \[\frac{d}{dx}\int_a^x f(t)dx=f(x)\] for all $a\le x\le b$.
+\end{theorem}
+
 \newpage
@@
 \label{sec:even_more_to_do}
-matrices
+- matrices
 
@@
 
+\newpage
+\listofmydefinitions
+
+\newpage
 \section{Acknowledgement}

### 2022-07-08 article.tex
Add theorems, corrolaries
Use package hyperref
Add hyperlinks

@@
 
+% very useful for hyperlinks
+\usepackage{hyperref}
+
 % to create a list of equations
@@
 \newtheorem{remark}[theorem]{Remark}
+\makeatletter
+\@addtoreset{theorem}{section}
+\makeatother
 
@@
 
+% create a list of theorems command
+\newcommand{\listtheoremsname}{List of Theorems}
+\newlistof{mytheorems}{thm}{\listtheoremsname}
+\newcommand{\mytheorems}[1]{%
+\addcontentsline{thm}{mytheorems}{\protect\numberline{\thetheorem}#1}\par}
+\renewcommand{\cftthmtitlefont}{\normalfont\Large\bfseries}
+
 % create a list of definitions command
@@
 \renewcommand{\cftdeftitlefont}{\normalfont\Large\bfseries}
+
+% create a list of corollaries command
+\newcommand{\listcorollariesname}{List of Corollaries}
+\newlistof{mycorollaries}{cor}{\listcorollariesname}
+\newcommand{\mycorollaries}[1]{%
+\addcontentsline{cor}{mycorollaries}{\protect\numberline{\thecorollary}#1}\par}
+\renewcommand{\cftcortitlefont}{\normalfont\Large\bfseries}
 
@@
 \label{sec:bold_italics_underline}
-Bold text is done with \textbackslash{textbf\{\textless text \textgreater\}} such as \textbf{bolded text}.
-
-Italics text is done with \textbackslash{textit\{\textless text \textgreater\}} such as \textit{italics text}.
-
-Underline text is done with \textbackslash{underline\{\textless text \textgreater\}} such as \underline{italics text}.
-
-Bold and italics text is done with \textbackslash{textbf\{\textbackslash{textit\{\textless text \textgreater\}\}} such as \textbf{\textit{bolded text}}.
-
 Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.
 
+\section{URLs}
+\label{sec:urls}
+Hyperlinks within the document can be easily added.
+For example, see Graphics \ref{sec:graphics} and Anatomy of a matplotlib figure \ref{fig:anatomy_of_a_matplotlib_figure} and Definition of a limit \ref{def:limit}.
+
+Hyperlinks to external URLs can be easily added. For example, see \href{https://en.wikipedia.org/wiki/Latex}{Wikipedia \LaTeX}.
 \section{Lists}
@@
 \begin{figure}[H]
-\label{fig:anatomy_of_a_matplotlib_figure}
 % \includegraphics[width=\textwidth, inner]{matplotlib_anatomy_of_a_figure}
@@
 \end{figure}
+\label{fig:anatomy_of_a_matplotlib_figure}
 
@@
 \end{theorem}
+\mytheorems{Fundamental theorem of calculus}
+
+\section{Corollaries}
+\label{sec:corollaries}
+\begin{corollary}
+If $f$ is continuous on the interval $[a,b]$, then \[\int_a^b f(x)dx=F(b)-F(a)\] where $F$ is any antiderivative of $f$.
+\end{corollary}
+\mycorollaries{f is continuous}
 
@@
 Blah blah \cite{JD} and blah blah \cite{JS} and blah blah \cite{JT}.
-
-\section{Still to do}
-\label{sec:still_to_do}
-
-\subsubsection{Not started}
-\label{sec:even_more_to_do}
-- matrices
 
@@
 \newpage
-\section{Acknowledgement}
-\label{sec:acknowledgement}
+\listofmytheorems
+
+\newpage
+\listofmycorollaries
+
+\newpage
+\section{Acknowledgements}
+\label{sec:acknowledgements}
 

### 2022-07-11 article.tex
Add subsections for list types
Add pmatrix, bmatrix
Add newpage for tidyness
Add lemmas
Add propositions
Revise to do
Move theorem definitions to preamble section
Re-order sections
Fix thebibliography indentation, add comments
Use bibtex

@@
 
+% this is the beginning of the preamble section
 % must always be first line of a <path.tex> document
@@
 \date{\today}
+% edit the following line for the title of the article
 \title{article title}
+% edit the following line for the author(s) of the article
 \author{article author}
@@
 
+% required for bibtex URLs
+\usepackage{url}
+
 % to create a list of equations
@@
 
-% useful for definitions, theorems, corollaries, etc.
+% define theorem-like elements
 \theoremstyle{myenv}
@@
 \newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{lemma}[theorem]{Lemma}
 \newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
 \newtheorem{axiom}[theorem]{Axiom}
@@
 \setlist[enumerate]{leftmargin=*}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-\end{abstract}
 
@@
 
+% create a list of lemmas command
+\newcommand{\listlemmasname}{List of Lemmas}
+\newlistof{mylemmas}{lem}{\listlemmasname}
+\newcommand{\mylemmas}[1]{%
+\addcontentsline{lem}{mylemmas}{\protect\numberline{\thelemma}#1}\par}
+\renewcommand{\cftlemtitlefont}{\normalfont\Large\bfseries}
+
+% create a list of propositions command
+\newcommand{\listpropositionsname}{List of Propositions}
+\newlistof{mypropositions}{prop}{\listpropositionsname}
+\newcommand{\mypropositions}[1]{%
+\addcontentsline{prop}{mypropositions}{\protect\numberline{\theproposition}#1}\par}
+\renewcommand{\cftproptitlefont}{\normalfont\Large\bfseries}
+
+% this is the end of the preamble section
+
+\begin{document}
+\maketitle
+
+\begin{abstract}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\end{abstract}
+
+\newpage
 \tableofcontents
@@
 \section{Lists}
-Unordered list
+\subsection{Unordered list}
+\label{sec:unordered_list}
 \begin{itemize}
@@
 
-Ordered list
+\subsection{Ordered list}
+\label{sec:ordered_list}
 \begin{enumerate}
@@
 
+\begin{flalign}
+A=\begin{pmatrix}
+1 &0 &4 &-1 \\
+0 &1 &-3 &1 \\
+0 &0 &0 &1
+\end{pmatrix}&&
+\end{flalign}
+
+\begin{flalign}
+A = \begin{bmatrix}
+1 &0 &4 &-1\\
+0 &1 &-3 &1 \\
+0 &0 &0 &1
+\end{bmatrix}&&
+\end{flalign}
+
+\newpage
+\section{Theorems}
+\label{sec:theorems}
+
+\begin{theorem}[Fundamental Theorem of Calculus]
+\label{thm:ftc}
+If $f$ is continuous on the interval $[a,b]$, then \[\frac{d}{dx}\int_a^x f(t)dx=f(x)\] for all $a\le x\le b$.
+\end{theorem}
+\mytheorems{Fundamental theorem of calculus}
+
 \section{Definitions}
@@
 
-\section{Theorems}
-\label{sec:theorems}
-
-\begin{theorem}[Fundamental Theorem of Calculus]
-\label{thm:ftc}
-If $f$ is continuous on the interval $[a,b]$, then \[\frac{d}{dx}\int_a^x f(t)dx=f(x)\] for all $a\le x\le b$.
-\end{theorem}
-\mytheorems{Fundamental theorem of calculus}
-
 \section{Corollaries}
@@
 \newpage
+\section{Lemmas}
+
+\label{sec:lemmas}
+\begin{lemma}
+$x+y=z$
+\end{lemma}
+\mylemmas{Lem 1}
+
+\begin{lemma}
+$z-r+t=3$
+\end{lemma}
+\mylemmas{Lem 2}
+
+\begin{lemma}
+$q=r$
+\end{lemma}
+\mylemmas{Lem 3}
+
+\begin{lemma}
+$x+y=z$
+\end{lemma}
+\mylemmas{Lem 4}
+
+\begin{lemma}
+$z-r+t=3$
+\end{lemma}
+\mylemmas{Lem 5}
+
+\begin{lemma}
+$q=r$
+\end{lemma}
+\mylemmas{Lem 6}
+
+\newpage
+\section{Propositions}
+
+\label{sec:propositions}
+\begin{proposition}
+$x+y=z$
+\end{proposition}
+\mypropositions{Prop 1}
+
+\begin{proposition}
+$\alpha=1-x$
+\end{proposition}
+\mypropositions{Prop 2}
+
+\newpage
 \section{Citations}
@@
 
-Blah blah \cite{JD} and blah blah \cite{JS} and blah blah \cite{JT}.
+The definitive book on MSA is by Wheeler \cite{wheeler2006}.
+The definitive book on SPC is by Wheeler \cite{wheeler2004}.
+The original article on Taguchi indices was by Russell Boyles \cite{boyles1991}.
+A very good article on the $C_\text{pm}$ index is found in Chen et.al.
+\cite{chan1988}.
+Gunter \cite{gunter1989}.
+
+\newpage
+\section{To do}
+
+\begin{itemize}
+    \item list to do items here
+\end{itemize}
 
@@
 \newpage
+\listofmytheorems
+
+\newpage
 \listofmydefinitions
@@
 \newpage
-\listofmytheorems
+\listofmycorollaries
 
 \newpage
-\listofmycorollaries
+\listofmylemmas
+
+\newpage
+\listofmypropositions
 
@@
 
-\begin{thebibliography}{99}
-\bibitem{JD} Doe, John. 2000. Title of book.
-\bibitem{JS} Smith, John. 2013. \textit{Title of article}.
-\bibitem{JT} Thomas, John. 2022. \textit{Online reference}.
-\end{thebibliography}
+\newpage
+\nocite{*}
+\bibliographystyle{plain}
+\bibliography{pilon_gilles}
 

### 2022-07-12 article.tex
Add, revise content
Refactor to use biblatex

@@
 
-% set references indent
+% useful for the bibliography
+\usepackage[style=numeric]{biblatex}
+\addbibresource{pilon_gilles.bib}
 
@@
 \label{sec:citations}
-The formatting of the bibliography is not quite what I wish. I will explore bibtex for this. For now, here is how to site articles, books, and online references.
 
-The definitive book on MSA is by Wheeler \cite{wheeler2006}.
+% The definitive book on MSA is by Wheeler \cite{wheeler2006}.
 The definitive book on SPC is by Wheeler \cite{wheeler2004}.
@@
 Gunter \cite{gunter1989}.
+
+Here is a single citation. \cite{wheeler2006}
 
@@
 \newpage
+\section{References}
 \nocite{*}
-\bibliographystyle{plain}
-\bibliography{pilon_gilles}
+\printbibliography[heading=none]
+\label{sec:references}
 

### 2022-07-13 article.tex
Refactor \cite

@@
 
-Here is a single citation. \cite{wheeler2006}
+Here is a single citation without prenote and postnote. The definitive book on MSA is by Wheeler \cite{wheeler2006}.
+
+Here is a single citation with prenote only. The definitive book on SPC is by \cite[Wheeler][]{wheeler2006}.
+
+Here is a single citation with prenote and postnote. For further details on $C_\text{pm}$, \cite[see][pages 1-10]{chan1988}.
 
@@
 \section{References}
-\nocite{*}
+% \nocite{*}
 \printbibliography[heading=none]

### 2022-07-14 article.tex
Change author, date font sizes
Add epigraph

@@
 \posttitle{\par\end{flushleft}}
-\preauthor{\begin{flushleft}\LARGE}
+\preauthor{\begin{flushleft}\normalsize}
 \postauthor{\end{flushleft}}
-\predate{\begin{flushleft}}
+\predate{\begin{flushleft}\small}
 \postdate{\end{flushleft}}
@@
 
+% useful for epigraphs
+\usepackage{epigraph}
+
 % this is the end of the preamble section
@@
 \label{sec:introduction}
+\renewcommand{\epigraphflush}{flushleft}
+\renewcommand{\textflush}{flushleft}
+\renewcommand{\sourceflush}{flushleft}
+\epigraph{Remember, the objective is to take the right action on the process. No
+credit is given for finding the `right numbers.'}{Donald J. Wheeler}
+
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 \label{sec:results}
+
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 \section{References}
-% \nocite{*}
+\nocite{*}
 \printbibliography[heading=none]

### 2022-07-19 article.tex
Add Greek letters for math, text

@@
 % very useful for hyperlinks
-\usepackage{hyperref}
+\usepackage[unicode]{hyperref}
+\hypersetup{
+    colorlinks=true,
+    urlcolor=blue
+}
+
+% useful for Greek letters in text mode
+\usepackage[cbgreek]{textgreek}
 
@@
 \renewcommand{\cftequtitlefont}{\normalfont\Large\bfseries}
+
+% create a list of Greek letters command
+\newcommand{\listgreekname}{List of Greek Letters}
+\newlistof{mygreek}{grk}{\listgreekname}
+\newcommand{\mygreek}[1]{%
+\addcontentsline{grk}{mygreek}{\protect\numberline{\thegreek}#1}\par}
+\renewcommand{\cftgrktitlefont}{\normalfont\Large\bfseries}
 
@@
     \item Illinois
-        \begin{itemize}
-            \item Chicago
-            \item Naperville
-        \end{itemize}
+        \begin{itemize} \item Chicago \item Naperville \end{itemize}
     \item Kentucky
-        \begin{itemize}
-            \item Lexington
-            \item Louisville
-        \end{itemize}
+        \begin{itemize} \item Lexington \item Louisville \end{itemize}
 \end{itemize}
@@
 \newpage
+\section{Greek letters}
+\label{sec:greek_letters}
+
+\subsection{Greek mathematics}
+\label{sec:greek_mathematics}
+
+alpha $\alpha$ A \\
+beta $\beta$ B \\
+gamma $\gamma$ $\Gamma$ \\
+delta $\delta$ $\Delta$ \\
+epsilon$\epsilon$ E \\
+zeta $\zeta$ Z \\
+eta $\eta$ H\\
+theta $\theta$ $\Theta$ \\
+iota $\iota$ I \\
+kappa $\kappa$ K \\
+lambda $\lambda$ $\Lambda$ \\
+mu $\mu$ M \\
+nu $\nu$ N \\
+xi $\xi$ $\Xi$ \\
+omicron o O \\
+pi $\pi$ $\Pi$\\
+rho $\rho$ P \\
+sgima $\sigma$ $\Sigma$ \\
+tau $\tau$ T \\
+upsilon $\upsilon$ $\Upsilon$ \\
+phi $\phi$ $\Phi$ \\
+chi $\chi$ X \\
+psi $\psi$ $\Psi$ \\
+omega $\omega$ $\Omega$ \\
+
+\subsection{Greek text}
+\label{sec:greek_text}
+
+alpha \textalpha \textAlpha \\
+beta \textbeta \textBeta \\
+gamma \textgamma \textGamma \\
+delta \textdelta \textDelta \\
+epsilon \textepsilon \textEpsilon \\
+zeta \textzeta \textZeta \\
+eta \texteta \textEta \\
+theta \texttheta \textTheta \\
+iota \textiota \textIota \\
+kappa \textkappa \textKappa \\
+lambda \textlambda \textLambda \\
+mu \textmu \textMu \\
+nu \textnu \textNu \\
+xi \textxi \textXi \\
+omicron o O \\
+pi \textpi \textPi \\
+rho \textrho \textRho \\
+sigma \textsigma \textSigma \\
+tau \texttau \textTau \\
+upsilon \textupsilon \textUpsilon \\
+phi \textphi \textPhi \\
+chi \textchi \textChi \\
+psi \textpsi \textPsi \\
+omega \textomega \textOmega \\
+
+\newpage
 \section{Theorems}

### 2022-07-19 article.tex
Add Greek unicode letters

@@
 
+\subsection{Greek unicode}
+\label{sec:greek_unicode}
+
+Greek letters can be inserted in mathematics and text using Unicode characters. In Neovim, the sequence is `ControlKey + v uhhhh` where `hhhh` is the Unicode.
+
+alpha 03b1 α 0391 Α \\
+beta 03b2 β 0392 Β \\
+gamma 03b3 γ 0393 Γ \\
+delta 03b4 δ 0394 Δ \\
+epsilon 03b5 ε 0395 Ε \\
+zeta 03b6 ζ 0396 Ζ \\
+eta 03b7 η 0397 Η \\
+theta 03b8 θ 0398 Θ \\
+iota 03b9 ι 0399 Ι \\
+kappa 03b1 α 039a Κ \\
+lambda 03bb λ 039b Λ \\
+mu 03bc μ 039c Μ \\
+nu 03bd ν 039d Ν \\
+xi 03be ξ 039e Ξ \\
+omicron o O \\
+pi 03c0 π 03ao Π \\
+rho 03c1 ρ 03a1 Ρ \\
+sigma 03c3 σ 03a3 Σ \\
+tau 03c4 τ 03a4 Τ \\
+upsilon 03c5 υ 03a5 Υ \\
+phi 03c6 φ 03a6 Φ \\
+chi 03c7 χ 03a7 Χ \\
+psi 03c8 ψ 03a8 Ψ \\
+omega 03c9 ω 03a9 Ω \\
+
 \subsection{Greek mathematics}

### 2022-07-19 article.tex
Convert Greek Unicode to table

--- 2022-07-19 article.tex
@@
 \usepackage{booktabs}
+\usepackage{multirow}
 
@@
 
+\subsection{Greek unicode}
+\label{sec:greek_unicode}
+
+Greek letters can be inserted in mathematics and text using Unicode characters. In Neovim, the sequence is `ControlKey + v uhhhh` where `hhhh` is the Unicode.
+
+\begin{table}[H]
+\begin{flushleft}
+\begin{tabular}{lcccc}
+\toprule
+letter & code & miniscule & code & majuscule \\
+\midrule
+alpha   & 03b1 & α & 0391 & Α \\
+beta    & 03b2 & β & 0392 & Β \\
+gamma   & 03b3 & γ & 0393 & Γ \\
+delta   & 03b4 & δ & 0394 & Δ \\
+epsilon & 03b5 & ε & 0395 & Ε \\
+zeta    & 03b6 & ζ & 0396 & Ζ \\
+eta     & 03b7 & η & 0397 & Η \\
+theta   & 03b8 & θ & 0398 & Θ \\
+iota    & 03b9 & ι & 0399 & Ι \\
+kappa   & 03b1 & α & 039a & Κ \\
+lambda  & 03bb & λ & 039b & Λ \\
+mu      & 03bc & μ & 039c & Μ \\
+nu      & 03bd & ν & 039d & Ν \\
+xi      & 03be & ξ & 039e & Ξ \\
+omicron &      & o &      & O \\
+pi      & 03c0 & π & 03ao & Π \\
+rho     & 03c1 & ρ & 03a1 & Ρ \\
+sigma   & 03c3 & σ & 03a3 & Σ \\
+tau     & 03c4 & τ & 03a4 & Τ \\
+upsilon & 03c5 & υ & 03a5 & Υ \\
+phi     & 03c6 & φ & 03a6 & Φ \\
+chi     & 03c7 & χ & 03a7 & Χ \\
+psi     & 03c8 & ψ & 03a8 & Ψ \\
+omega   & 03c9 & ω & 03a9 & Ω \\
+\bottomrule
+\end{tabular}
+\end{flushleft}
+\end{table}
+
 \subsection{Greek mathematics}

### 2022-07-19 article.tex
Convert Greek mathematics to table

@@
 
-\subsection{Greek unicode}
+\subsection{Greek Unicode}
 \label{sec:greek_unicode}
@@
 \end{tabular}
+\label{tab:greek_unicode}
+\caption{Greek Unicode}
 \end{flushleft}
@@
 
-alpha $\alpha$ A \\
-beta $\beta$ B \\
-gamma $\gamma$ $\Gamma$ \\
-delta $\delta$ $\Delta$ \\
-epsilon$\epsilon$ E \\
-zeta $\zeta$ Z \\
-eta $\eta$ H\\
-theta $\theta$ $\Theta$ \\
-iota $\iota$ I \\
-kappa $\kappa$ K \\
-lambda $\lambda$ $\Lambda$ \\
-mu $\mu$ M \\
-nu $\nu$ N \\
-xi $\xi$ $\Xi$ \\
-omicron o O \\
-pi $\pi$ $\Pi$\\
-rho $\rho$ P \\
-sgima $\sigma$ $\Sigma$ \\
-tau $\tau$ T \\
-upsilon $\upsilon$ $\Upsilon$ \\
-phi $\phi$ $\Phi$ \\
-chi $\chi$ X \\
-psi $\psi$ $\Psi$ \\
-omega $\omega$ $\Omega$ \\
+Greek letters can be inserted in mathematics. These are naturally italicized.
+
+\begin{table}[H]
+\begin{flushleft}
+\begin{tabular}{lcccc}
+\toprule
+letter & code & miniscule & code & majuscule \\
+\midrule
+alpha   & \$\textbackslash alpha\$   & $\alpha$   & \$A\$                      & $A$ \\
+beta    & \$\textbackslash beta\$    & $\beta$    & \$B\$                      & $B$ \\
+gamma   & \$\textbackslash gamma\$   & $\gamma$   & \$\textbackslash Gamma\$   & $\Gamma$ \\
+delta   & \$\textbackslash delta\$   & $\delta$   & \$\textbackslash Delta\$   & $\Delta$ \\
+epsilon & \$\textbackslash epsilon\$ & $\epsilon$ & \$E\$                      & $E$ \\
+zeta    & \$\textbackslash zeta\$    & $\zeta$    & \$Z\$                      & $Z$ \\
+eta     & \$\textbackslash eta\$     & $\eta$     & \$H\$                      & $H$ \\
+theta   & \$\textbackslash theta\$   & $\theta$   & \$\textbackslash Theta\$   & $\Theta$ \\
+iota    & \$\textbackslash iota\$    & $\iota$    & \$I\$                      & $I$ \\
+kappa   & \$\textbackslash kappa\$   & $\kappa$   & \$K\$                      & $K$ \\
+lambda  & \$\textbackslash lambda\$  & $\lambda$  & \$\textbackslash Lambda\$  & $\Lambda$ \\
+mu      & \$\textbackslash mu\$      & $\mu$      & \$M\$                      & $M$ \\
+nu      & \$\textbackslash nu\$      & $\nu$      & \$N\$                      & $N$ \\
+xi      & \$\textbackslash xi\$      & $\xi$      & \$\textbackslash Xi\$      & $\Xi$ \\
+omicron & \$o\$                      & $o$        & \$O\$                      & $O$ \\
+pi      & \$\textbackslash pi\$      & $\pi$      & \$\textbackslash Pi\$      & $\Pi$ \\
+rho     & \$\textbackslash rho\$     & $\rho$     & \$P\$                      & $P$ \\
+sigma   & \$\textbackslash sigma\$   & $\sigma$   & \$\textbackslash Sigma\$   & $\Sigma$ \\
+tau     & \$\textbackslash tau\$     & $\tau$     & \$T\$                      & $T$ \\
+upsilon & \$\textbackslash upsilon\$ & $\upsilon$ & \$\textbackslash Upsilon\$ & $\Upsilon$ \\
+phi     & \$\textbackslash phi\$     & $\phi$     & \$\textbackslash Phi\$     & $\Phi$ \\
+chi     & \$\textbackslash chi\$     & $\chi$     & \$X\$                      & $X$ \\
+psi     & \$\textbackslash psi\$     & $\psi$     & \$\textbackslash Psi\$     & $\Psi$ \\
+omega   & \$\textbackslash omega\$   & $\omega$   & \$\textbackslash Omega\$   & $\Omega$ \\
+\bottomrule
+\end{tabular}
+\label{tab:greek_mathematics}
+\caption{Greek mathematics}
+\end{flushleft}
+\end{table}
 

### 2022-07-19 article.tex
Convert Greek text to table

@@
 
+\newpage
 \subsection{Greek mathematics}
@@
 
+\newpage
 \subsection{Greek text}
@@
 
-alpha \textalpha \textAlpha \\
-beta \textbeta \textBeta \\
-gamma \textgamma \textGamma \\
-delta \textdelta \textDelta \\
-epsilon \textepsilon \textEpsilon \\
-zeta \textzeta \textZeta \\
-eta \texteta \textEta \\
-theta \texttheta \textTheta \\
-iota \textiota \textIota \\
-kappa \textkappa \textKappa \\
-lambda \textlambda \textLambda \\
-mu \textmu \textMu \\
-nu \textnu \textNu \\
-xi \textxi \textXi \\
-omicron o O \\
-pi \textpi \textPi \\
-rho \textrho \textRho \\
-sigma \textsigma \textSigma \\
-tau \texttau \textTau \\
-upsilon \textupsilon \textUpsilon \\
-phi \textphi \textPhi \\
-chi \textchi \textChi \\
-psi \textpsi \textPsi \\
-omega \textomega \textOmega \\
+Greek letters can be inserted as text.
+
+\begin{table}[H]
+\begin{flushleft}
+\begin{tabular}{lcccc}
+\toprule
+letter & code & miniscule & code & majuscule \\
+\midrule
+alpha    & \textbackslash textalpha   & \textalpha   & \textbackslash textAlpha   & \textAlpha \\
+beta     & \textbackslash textbeta    & \textbeta    & \textbackslash textBeta    & \textBeta \\
+gamma    & \textbackslash textgamma   & \textgamma   & \textbackslash textGamma   & \textGamma \\
+delta    & \textbackslash textdelta   & \textdelta   & \textbackslash textDelta   & \textDelta \\
+epsilon  & \textbackslash textepsilon & \textepsilon & \textbackslash textEpsilon & \textEpsilon \\
+zeta     & \textbackslash textzeta    & \textzeta    & \textbackslash textZeta    & \textZeta \\
+eta      & \textbackslash texteta     & \texteta     & \textbackslash textEta     & \textEta \\
+theta    & \textbackslash texttheta   & \texttheta   & \textbackslash textTheta   & \textTheta \\
+iota     & \textbackslash textiota    & \textiota    & \textbackslash textIota    & \textIota \\
+kappa    & \textbackslash textkappa   & \textkappa   & \textbackslash textKappa   & \textKappa \\
+lambda   & \textbackslash textlambda  & \textlambda  & \textbackslash textLambda  & \textLambda \\
+mu       & \textbackslash textmu      & \textmu      & \textbackslash textMu      & \textMu \\
+nu       & \textbackslash textnu      & \textnu      & \textbackslash textNu      & \textNu \\
+xi       & \textbackslash textxi      & \textxi      & \textbackslash textXi      & \textXi \\
+omicrdon & o                          & o            & O                          & O \\
+pi       & \textbackslash textpi      & \textpi      & \textbackslash textPi      & \textPi \\
+rho      & \textbackslash textrho     & \textrho     & \textbackslash textRho     & \textRho \\
+sigma    & \textbackslash textsigma   & \textsigma   & \textbackslash textSigma   & \textSigma \\
+tau    & \textbackslash texttau   & \texttau   & \textbackslash textTau   & \textTau \\
+upsilon    & \textbackslash textupsilon   & \textupsilon   & \textbackslash textUpsilon   & \textUpsilon \\
+phi    & \textbackslash textphi   & \textphi   & \textbackslash textPhi   & \textPhi \\
+chi    & \textbackslash textchi   & \textchi   & \textbackslash textChi   & \textChi \\
+psi    & \textbackslash textpsi   & \textpsi   & \textbackslash textPsi   & \textPsi \\
+omega    & \textbackslash textomega   & \textomega   & \textbackslash textOmega   & \textOmega \\
+\bottomrule
+\end{tabular}
+\label{tab:greek_text}
+\caption{Greek text}
+\end{flushleft}
+\end{table}
 

### 2022-07-19 article.tex
Refactor links using hyperref, hypersetup

@@
 % very useful for hyperlinks
-\usepackage[unicode]{hyperref}
-\hypersetup{
-    colorlinks=true,
-    urlcolor=blue
-}
-
 % useful for Greek letters in text mode
 \usepackage[cbgreek]{textgreek}
-
-% required for bibtex URLs
-\usepackage{url}
 
@@
 
+\usepackage[unicode]{hyperref}
+\hypersetup{
+    colorlinks=true,
+    urlcolor=magenta,
+    citecolor=green,
+    linkcolor=red
+}
+
 % this is the end of the preamble section
@@
 Hyperlinks within the document can be easily added.
-For example, see Graphics \ref{sec:graphics} and Anatomy of a matplotlib figure \ref{fig:anatomy_of_a_matplotlib_figure} and Definition of a limit \ref{def:limit}.
+For example, \hyperref[sec:graphics]{see Graphics} and \hyperref[fig:anatomy_of_a_matplotlib_figure]{Anatomy of a matplotlib figure} and \hyperref[def:limit]{Definition of a limit}.
 
@@
 \newpage
-\section{To do}
-
-\begin{itemize}
-    \item list to do items here
-\end{itemize}
-
-\newpage
 \listoffigures

### 2022-07-19 article.tex
Tidy tables, correct kappa miniscule

@@
 iota    & 03b9 & ι & 0399 & Ι \\
-kappa   & 03b1 & α & 039a & Κ \\
+kappa   & 03ba & κ & 039a & Κ \\
 lambda  & 03bb & λ & 039b & Λ \\

### 2022-07-20 article.tex
Refactor tables

@@
 
+\subsection{Simple table}
+\label{sec:simple_table}`
+
 \begin{table}[H]
@@
 
+\subsection{Multirow table}
+\label{sec:multirow_table}`
 \begin{table}[H]
-\begin{flushleft}
-\begin{tabular}{ccc}
+\footnotesize
+\centering
+\begin{tabular}{llll}
 \toprule
-$A$      & $B$ & $ A \land B$ \\
+                                           & \textbf{Process requirement}            & \textbf{Sampling}                        & \textbf{Comments} \\
 \midrule
-T        & T   & T \\
-T        & F   & F \\
-F        & T   & F \\
-F        & F   & F \\
+\multirow[t]{4}{*}{$C_\text{pk}$}          & - Stable and predictable variation      & - Rational                               & - Possible cost to increasing $C_\text{pk}$ \\
+                                           & - Normal distribution                   & - Representative of process              & - Wide confidence interval \\
+                                           & - Need at least one specification limit & - Ensure same process conditions         & \\
+                                           &                                         & - No identifiable condition changes      & \\
+\multirow[t]{4}{*}{$P_\text{pk}$}          & - Stable and predictable variation      & - Random                                 & - Possible cost to increasing ppk \\
+                                           & - Normal distribution                   & - Sufficiently large, representative     & - Wide confidence interval \\
+                                           & - Need at least one specification limit & - Ensure same process conditions         & - Easiest formulae to explain \\
+                                           &                                         & - No identifiable condition changes      & \\
+\multirow[t]{4}{*}{$C_\text{pm}$}          & - Stable and predictable variation      & - Same as $C_\text{pk}$ or $P_\text{pk}$ & - $C_\text{pm}$ penalizes for being off-target \\
+                                           & - Normal distribution                   &                                          & - Wide confidence interval \\
+                                           & - Need at least one specification limit &                                          & - Most difficult formulae to explain \\
+                                           & - Need specification target             &                                          & \\
 \bottomrule
 \end{tabular}
-\label{tab:boolean_truth_table}
-\caption{Boolean truth table}
-\end{flushleft}
+\caption{Comparison of capability indices}
+\label{tab:comparison_capability_indices}
 \end{table}

### 2022-07-20 article.tex
Refactor citations for authoryear style

@@
 % useful for the bibliography
-\usepackage[style=numeric]{biblatex}
+\usepackage[style=authoryear]{biblatex}
 \addbibresource{pilon_gilles.bib}
@@
 
-% The definitive book on MSA is by Wheeler \cite{wheeler2006}.
-The definitive book on SPC is by Wheeler \cite{wheeler2004}.
-The original article on Taguchi indices was by Russell Boyles \cite{boyles1991}.
-A very good article on the $C_\text{pm}$ index is found in Chen et.al.
-\cite{chan1988}.
-Gunter \cite{gunter1989}.
+Here is a single citation without prenote and postnote. There is a definitive book on MSA (\cite{wheeler2006}).
 
-Here is a single citation without prenote and postnote. The definitive book on MSA is by Wheeler \cite{wheeler2006}.
+Here is a single citation with prenote only. There is a definitive book on SPC (\cite[see][]{wheeler2006}).
 
-Here is a single citation with prenote only. The definitive book on SPC is by \cite[Wheeler][]{wheeler2006}.
-
-Here is a single citation with prenote and postnote. For further details on $C_\text{pm}$, \cite[see][pages 1-10]{chan1988}.
+Here is a single citation with postnote only. $C_\text{pm}$ is a complex subject (\cite[][pages 1-10]{chan1988}).
 

### 2022-07-20 article.tex
Tidy section, subsection lables

@@
 \newpage
-\section{Introduction}
-\label{sec:introduction}
+\section{Introduction}\label{sec:introduction}
 \renewcommand{\epigraphflush}{flushleft}
@@
 
-\section{Prior research}
-\label{sec:prior_research}
+\section{Prior research}\label{sec:prior_research}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 
-\section{Results}
-\label{sec:results}
+\section{Results}\label{sec:results}
 
@@
 \newpage
-\section{Bold, italics, and underline}
-\label{sec:bold_italics_underline}
+\section{Bold, italics, and underline}\label{sec:bold_italics_underline}
 Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.
 
-\section{URLs}
-\label{sec:urls}
+\section{URLs}\label{sec:urls}
 Hyperlinks within the document can be easily added.
@@
 Hyperlinks to external URLs can be easily added. For example, see \href{https://en.wikipedia.org/wiki/Latex}{Wikipedia \LaTeX}.
-\section{Lists}
-\subsection{Unordered list}
-\label{sec:unordered_list}
+\section{Lists}\label{sec:lists}
+\subsection{Unordered list}\label{sec:unordered_list}
 \begin{itemize}
@@
 
-\subsection{Ordered list}
-\label{sec:ordered_list}
+\subsection{Ordered list}\label{sec:ordered_list}
 \begin{enumerate}
@@
 \newpage
-\section{Graphics}
-\label{sec:graphics}
+\section{Graphics}\label{sec:graphics}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 \newpage
-\section{Tables}
-\label{sec:tables}
+\section{Tables}\label{sec:tables}
 
-\subsection{Simple table}
-\label{sec:simple_table}`
+\subsection{Simple table}\label{sec:simple_table}`
 
@@
 
-\subsection{Multirow table}
-\label{sec:multirow_table}`
+\subsection{Multirow table}\label{sec:multirow_table}`
 \begin{table}[H]
@@
 \newpage
-\section{Mathematics}
-\label{sec:mathematics}
+\section{Mathematics}\label{sec:mathematics}
 
-\subsection{Inline mathematics}
-\label{sec:inline_mathematics}`
+\subsection{Inline mathematics}\label{sec:inline_mathematics}`
 Examples of inline mathematics $\frac{a}{b}$, followed by text and another inline equation $\lim_{x\to 0}\frac{\sin x}{x}$=1 and more text $\sum_{k=0}^\infty \frac{1}{2^k}=2$ and finally much more text to cover many lines of a paragraph.
 
-\subsection{Display-style mathematics}
-\label{sec:display_style_mathematics}
+\subsection{Display-style mathematics}\label{sec:display_style_mathematics}
 Examples of mathematics on their own lines.
@@
 \newpage
-\section{Greek letters}
-\label{sec:greek_letters}
+\section{Greek letters}\label{sec:greek_letters}
 
-\subsection{Greek Unicode}
-\label{sec:greek_unicode}
+\subsection{Greek Unicode}\label{sec:greek_unicode}
 
@@
 \newpage
-\subsection{Greek mathematics}
-\label{sec:greek_mathematics}
+\subsection{Greek mathematics}\label{sec:greek_mathematics}
 
@@
 \newpage
-\subsection{Greek text}
-\label{sec:greek_text}
+\subsection{Greek text}\label{sec:greek_text}
 
@@
 \newpage
-\section{Theorems}
-\label{sec:theorems}
+\section{Theorems}\label{sec:theorems}
 
@@
 
-\section{Definitions}
-\label{sec:definitions}
+\section{Definitions}\label{sec:definitions}
 
@@
 
-\section{Corollaries}
-\label{sec:corollaries}
+\section{Corollaries}\label{sec:corollaries}
 \begin{corollary}
@@
 \newpage
-\section{Lemmas}
-
-\label{sec:lemmas}
+\section{Lemmas}\label{sec:lemmas}
 \begin{lemma}
@@
 \newpage
-\section{Propositions}
-
-\label{sec:propositions}
+\section{Propositions}\label{sec:propositions}
 \begin{proposition}
@@
 \newpage
-\section{Citations}
-\label{sec:citations}
+\section{Citations}\label{sec:citations}
 
@@
 \newpage
-\section{Acknowledgements}
-\label{sec:acknowledgements}
+\section{Acknowledgements}\label{sec:acknowledgements}
 
@@
 
-\section{Supporting information}
-\label{sec:supporting_information}
+\section{Supporting information}\label{sec:supporting_information}
 
@@
 \newpage
-\section{References}
+\section{References}\label{sec:references}
 \nocite{*}
 \printbibliography[heading=none]
-\label{sec:references}
 

### 2022-07-21 pilon_gilles_glossary.tex
Create pilon_gilles_glossary.tex

\newglossaryentry{process_capability}
{
    name={process capability},
    description={The ability of a process to meet a performance standard}
}
\newglossaryentry{process_capability_index}
{
    name={process capability index},
    description={The ratio of a specification measure and a dispersion measure},
    plural={process capability indices}
}
\newdualentry{msa}{MSA}{Measurement System Analysis}{Methods to evaluate measurements systems, to understand the causes of measurement variation}
\newglossaryentry{test_retest_error}
{
    name={test-retest error},
    description={The standard deviation of making repeated measurements of the same characteristic on the same parts with the same measuring instrument}
}
\newglossaryentry{probable_error}
{
    name={probable error},
    description={TBD}
}
\newdualentry{icc}{ICC}{intraclass correlation coefficient}{Describes how strongly units in the same group resemble each other}
\newglossaryentry{statistical_control}
{
    name={statistical control},
    description={A process is said to be in a state of statistical control if the variation for both charts is stable and predictable. This means that no points fail various control chart rules and no systematic patterns of variation are present.}
}
\newglossaryentry{distance_to_nearest_specification}
{
    name={distance to nearest specification (sigma level)},
    description={The difference between the location statistic and the closest specification limit, divided by the dispersion statistic (e.g. the standard deviation)}
}
\newglossaryentry{hypothesis_test}
{
    name={hypothesis test},
    description={A method for proving that an observed difference was not due to random chance},
    plural={hypothesis tests}
}
\newglossaryentry{dot_plot}
{
    name={dot plot},
    description={A chart in which dots are used to depict the quantitative values (e.g. counts) associated with categorical variables},
    plural={dot plots}
}
\newglossaryentry{normal_distribution}
{
    name={normal distribution},
    description={A type of continuous probability distribution for a real-valued random variable},
    plural={normal distributions}
}
\newglossaryentry{confidence_interval}
{
    name={confidence interval},
    description={It is an interval calculated from values in a sample. The interval is constructed for a specified probability of containing the unknown true value of a population parameter.
    },
    plural={confidence intervals}
}

### 2022-07-22 pilon_gilles_glossary.tex
Add new terms

@@
 }
+\newdualentry{anome}{ANOME}{analysis of main effects}{A chart that compares the average of each level to the overall average}
+\newdualentry{anomr}{ANOMR}{analysis of mean ranges}{A chart that compares the average range of each level to the overall range}
+\newdualentry{pp}{$P_\text{p}$}{process capability index two-sided (random sample)}{Compares the width of the process specification to the width of the process variation}
+\newdualentry{ppk}{$P_\text{pk}$}{process capability index one-sided (random sample)}{Calculates the distance from each specification limit to the average and compares then to the width of the process variation}
+\newdualentry{cp}{$C_\text{p}$}{process capability index two-sided (rational sample)}{Compares the width of the process specification to the width of the process variation}
+\newdualentry{cpk}{$C_\text{pk}$}{process capability index one-sided (rational sample)}{Calculates the distance from each specification limit to the average and compares then to the width of the process variation}
+\newdualentry{cpm}{$C_\text{pm}$}{process capability index loss function (random sample)}{Calculates process capability with respect to deviation from the average and deviation from the target}

### 2022-07-22 pilon_gilles_glossary.tex
Sort entries by label
Add dependent variable
Add independent variable

@@
+\newdualentry{anome}{ANOME}{analysis of main effects}{A chart that compares the average of each level to the overall average}
+\newdualentry{anomr}{ANOMR}{analysis of mean ranges}{A chart that compares the average range of each level to the overall range}
+\newdualentry{cp}{$C_\text{p}$}{process capability index two-sided (rational sample)}{Compares the width of the process specification to the width of the process variation}
+\newdualentry{cpk}{$C_\text{pk}$}{process capability index one-sided (rational sample)}{Calculates the distance from each specification limit to the average and compares then to the width of the process variation}
+\newdualentry{cpm}{$C_\text{pm}$}{process capability index loss function (random sample)}{Calculates process capability with respect to deviation from the average and deviation from the target}
+\newdualentry{icc}{ICC}{intraclass correlation coefficient}{Describes how strongly units in the same group resemble each other}
+\newdualentry{msa}{MSA}{Measurement System Analysis}{Methods to evaluate measurements systems, to understand the causes of measurement variation}
+\newdualentry{pp}{$P_\text{p}$}{process capability index two-sided (random sample)}{Compares the width of the process specification to the width of the process variation}
+\newdualentry{ppk}{$P_\text{pk}$}{process capability index one-sided (random sample)}{Calculates the distance from each specification limit to the average and compares then to the width of the process variation}
+\newglossaryentry{confidence_interval}
+{
+    name={confidence interval},
+    description={It is an interval calculated from values in a sample. The interval is constructed for a specified probability of containing the unknown true value of a population parameter.
+    },
+    plural={confidence intervals}
+}
+\newglossaryentry{dependent_variable}
+{
+    name={dependent variable},
+    description={The result of varying the values of other variables. In $y = mX + b$, y is the dependent variable.},
+    plural={dependent variables}
+}
+\newglossaryentry{distance_to_nearest_specification}
+{
+    name={distance to nearest specification (sigma level)},
+    description={The difference between the location statistic and the closest specification limit, divided by the dispersion statistic (e.g. the standard deviation)}
+}
+\newglossaryentry{dot_plot}
+{
+    name={dot plot},
+    description={A chart in which dots are used to depict the quantitative values (e.g. counts) associated with categorical variables},
+    plural={dot plots}
+}
+\newglossaryentry{hypothesis_test}
+{
+    name={hypothesis test},
+    description={A method for proving that an observed difference was not due to random chance},
+    plural={hypothesis tests}
+}
+\newglossaryentry{independent_variable}
+{
+    name={independent variable},
+    description={The values that are deliberately or randomly changed. In $y = mX + b$, x is the independent variable.},
+    plural={dependent variables}
+}
+\newglossaryentry{normal_distribution}
+{
+    name={normal distribution},
+    description={A type of continuous probability distribution for a real-valued random variable},
+    plural={normal distributions}
+}
 \newglossaryentry{process_capability}
@@
 }
-\newdualentry{msa}{MSA}{Measurement System Analysis}{Methods to evaluate measurements systems, to understand the causes of measurement variation}
-\newglossaryentry{test_retest_error}
-{
-    name={test-retest error},
-    description={The standard deviation of making repeated measurements of the same characteristic on the same parts with the same measuring instrument}
-}
 \newglossaryentry{probable_error}
@@
 }
-\newdualentry{icc}{ICC}{intraclass correlation coefficient}{Describes how strongly units in the same group resemble each other}
 \newglossaryentry{statistical_control}
@@
 }
-\newglossaryentry{distance_to_nearest_specification}
+\newglossaryentry{test_retest_error}
 {
-    name={distance to nearest specification (sigma level)},
-    description={The difference between the location statistic and the closest specification limit, divided by the dispersion statistic (e.g. the standard deviation)}
+    name={test-retest error},
+    description={The standard deviation of making repeated measurements of the same characteristic on the same parts with the same measuring instrument}
 }
-\newglossaryentry{hypothesis_test}
-{
-    name={hypothesis test},
-    description={A method for proving that an observed difference was not due to random chance},
-    plural={hypothesis tests}
-}
-\newglossaryentry{dot_plot}
-{
-    name={dot plot},
-    description={A chart in which dots are used to depict the quantitative values (e.g. counts) associated with categorical variables},
-    plural={dot plots}
-}
-\newglossaryentry{normal_distribution}
-{
-    name={normal distribution},
-    description={A type of continuous probability distribution for a real-valued random variable},
-    plural={normal distributions}
-}
-\newglossaryentry{confidence_interval}
-{
-    name={confidence interval},
-    description={It is an interval calculated from values in a sample. The interval is constructed for a specified probability of containing the unknown true value of a population parameter.
-    },
-    plural={confidence intervals}
-}
-\newdualentry{anome}{ANOME}{analysis of main effects}{A chart that compares the average of each level to the overall average}
-\newdualentry{anomr}{ANOMR}{analysis of mean ranges}{A chart that compares the average range of each level to the overall range}
-\newdualentry{pp}{$P_\text{p}$}{process capability index two-sided (random sample)}{Compares the width of the process specification to the width of the process variation}
-\newdualentry{ppk}{$P_\text{pk}$}{process capability index one-sided (random sample)}{Calculates the distance from each specification limit to the average and compares then to the width of the process variation}
-\newdualentry{cp}{$C_\text{p}$}{process capability index two-sided (rational sample)}{Compares the width of the process specification to the width of the process variation}
-\newdualentry{cpk}{$C_\text{pk}$}{process capability index one-sided (rational sample)}{Calculates the distance from each specification limit to the average and compares then to the width of the process variation}
-\newdualentry{cpm}{$C_\text{pm}$}{process capability index loss function (random sample)}{Calculates process capability with respect to deviation from the average and deviation from the target}

### 2022-07-23 pilon_gilles_glossary.tex
Fix error in independent plural
Update probable error description
Add Taguchi Loss Function

@@
     description={The values that are deliberately or randomly changed. In $y = mX + b$, x is the independent variable.},
-    plural={dependent variables}
+    plural={independent variables}
 }
@@
     name={probable error},
-    description={TBD}
+    description={Also called resolution. It is the interval within which a single measurement might occur 50 \% of the time, $\pm 0.6745 \times \sigma_\text{pure error}$}
 }
@@
 }
+\newglossaryentry{taguchi_loss_function}
+{
+    name={Taguchi Loss Function},
+    description={It is a graphical depiction of loss to describe a phenomenon affecting the value of products produced by a company.
+It was developed by the Japanese business statistician Genichi Taguchi.}
+}
 \newglossaryentry{test_retest_error}

### 2022-07-23 pilon_gilles_glossary.tex
Revise confidence interval

@@
     name={confidence interval},
-    description={It is an interval calculated from values in a sample. The interval is constructed for a specified probability of containing the unknown true value of a population parameter.
+    description={In frequentist statistics, it is a range of estimates for an unknown parameter, interval calculated from values in a sample.
     },

### 2022-07-23 pilon_gilles_glossary.tex
Add outlier
Add type I error

@@
 }
+\newglossaryentry{outlier}
+{
+    name={outlier},
+    description={It is a data point that differs significantly from other observations.
+An outlier may be due to variability in the measurement or it may indicate experimental error.
+An outlier can cause serious problems in statistical analyses.},
+    plural={outliers}
+}
 \newglossaryentry{process_capability}
@@
 }
+\newglossaryentry(type_i_error},
+{
+    name={type I error},
+    description={It is the probability of saying something is different when in fact it is not.
+We find a difference that isn’t really there.
+It is also called alpha risk, producer's risk, and false positive.},
+    plural={Type I errors}
+}

### 2022-07-23 pilon_gilles_glossary.tex
Add type II error

@@
 }
+\newglossaryentry(type_ii_error},
+{
+    name={type II error},
+    description={It is the probability of saying something is not different when in fact it is.
+We fail to find a difference when there is one.
+It is also called beta risk, consumer’s risk, and false negative.
+It is used to calculate the power of the test (1-beta), as well as in calculations of sample size.},
+    plural={Type I errors}
+}

### 2022-07-24 pilon_gilles_glossary.tex
Fix typos
Add chi-square distribution
Add distance to target
Add process behaviour chart

@@
 \newdualentry{ppk}{$P_\text{pk}$}{process capability index one-sided (random sample)}{Calculates the distance from each specification limit to the average and compares then to the width of the process variation}
+\newglossaryentry{chi_square_distribution}
+{
+    name={chi-square distribution},
+    description={It is the distribution of a sum of the squares of k independent standard normal random variables with k degrees of freedom.},
+    plural={chi-square distributions}
+}
 \newglossaryentry{confidence_interval}
@@
     description={The difference between the location statistic and the closest specification limit, divided by the dispersion statistic (e.g. the standard deviation)}
+}
+\newglossaryentry{distance_to_target}
+{
+    name={distance to target},
+    description={The difference between the specification target and the average is the difference you must adjust to aim the process correctly.}
 }
@@
 }
+\newglossaryentry{process_behaviour_chart}
+{
+    name={process behaviour chart},
+    description={It is used to determine if the variation of a sample statistic of a process is stable and predictable, that is, in a state of statistical control.
+It is also called a Shewhart chart and a control chart.}
+    plural={process behaviour charts}
+}
 \newglossaryentry{statistical_control}
@@
 }
-\newglossaryentry(type_i_error},
+\newglossaryentry{type_i_error}
 {
@@
 }
-\newglossaryentry(type_ii_error},
+\newglossaryentry{type_ii_error}
 {
@@
 It is used to calculate the power of the test (1-beta), as well as in calculations of sample size.},
-    plural={Type I errors}
+    plural={Type II errors}
 }

### 2022-07-25 pilon_gilles_glossary.tex
Add sources of variation
Add range chart

@@
 }
+\newglossaryentry{range_chart}
+{
+    name={range chart},
+    description={It is a chart that plots the range of a subgroup of values taken in a rational manner.
+The chart also has an upper control limit line, a lower control limit line, and an average line.},
+    plural={range charts}
+}
+\newglossaryentry{sources_of_variation}
+{
+    name={sources of variation},
+    description={These are the factors in a process that cause variation on the dependent variable.
+These factors may vary in a deliberate manner (fixed effects), random manner (random effects), or mixed effects (fixed and random factors)}
+}
 \newglossaryentry{statistical_control}

### 2022-07-25 pilon_gilles_glossary.tex
Add average chart
Add parallelism chart

@@
 \newdualentry{ppk}{$P_\text{pk}$}{process capability index one-sided (random sample)}{Calculates the distance from each specification limit to the average and compares then to the width of the process variation}
+\newglossaryentry{average_chart}
+{
+    name={average chart},
+    description={It is a process behaviour chart that plots the average of a subgroup of values taken in a rational manner.
+The chart also has an upper control limit line, a lower control limit line and an average line.},
+    plural={average charts}
+}
 \newglossaryentry{chi_square_distribution}
@@
 }
+\newglossaryentry{parallelism_chart}
+{
+    name={parallelism chart},
+    description={It is a process behaviour chart that plots the lines from the average chart and puts them on top of each other.
+It is used in measurement system analysis.
+Differences for any part indicate an operator bias relative to other operators.},
+    plural={parallelism charts}
+}
 \newglossaryentry{process_capability}
@@
     name={range chart},
-    description={It is a chart that plots the range of a subgroup of values taken in a rational manner.
+    description={It is a process behaviour chart that plots the range of a subgroup of values taken in a rational manner.
 The chart also has an upper control limit line, a lower control limit line, and an average line.},

### 2022-07-25 pilon_gilles_glossary.tex
Add individuals chart
Add moving range chart

@@
     description={It is a process behaviour chart that plots the average of a subgroup of values taken in a rational manner.
-The chart also has an upper control limit line, a lower control limit line and an average line.},
+The chart also has an upper control limit line, a lower control limit line, and an average line.},
     plural={average charts}
@@
     plural={independent variables}
+}
+\newglossaryentry{individuals_chart}
+{
+    name={individuals chart},
+    description={It is a process behaviour chart that plots the single values taken in a rational manner.
+The chart also has an upper control limit line, a lower control limit line, and an average line.},
+    plural={individuals charts}
+}
+\newglossaryentry{moving_range_chart}
+{
+    name={moving range chart},
+    description={It is a process behaviour chart that plots the difference between successive pairs of values taken in a rational manner.
+The chart also has an upper control limit line, a lower control limit line, and an average line.}
+    plural={moving range charts}
 }

### 2022-07-25 pilon_gilles_glossary.tex
Add specification
Add plural to specification
Add variance

@@
 }
+\newglossaryentry{specification}
+{
+    name={specification},
+    description={In the context of measurement system analysis, process capability, and process control, a specification is a lower limit, a target, and an upper limit},
+    plural={specifications}
+}
 \newglossaryentry{statistical_control}
@@
 }
+\newglossaryentry{variance}
+{
+    name={variance},
+    description={It is a measure of dispersion, how far a set of numbers is spread out from their average.
+It is the expectation of the squared devitaion of a random variable from its population average or sample saverage.}
+    plural={variances}
+}

### 2022-07-25 pilon_gilles_glossary.tex
Update statistical control
Add Nelson's Rules

@@
 }
+\newglossaryentry{nelsons_rules}
+{
+    name={Nelson's Rules},
+    description={They are a set of process behaviour chart rules for assessing statistical control.}
+}
 \newglossaryentry{normal_distribution}
@@
     description={A process is said to be in a state of statistical control if the variation for both charts is stable and predictable.
-This means that no points fail various control chart rules and no systematic patterns of variation are present.}
+This means that no points fail various control chart rules, such as Nelson's rules, and no systematic patterns of variation are present.
+It is also called process stability.}
 }

### 2022-08-06 article.tex
Rename bibliography input file
Fix most errors to make article work

@@
 % this is the beginning of the preamble section
-% must always be first line of a <path.tex> document
+% the next line must always be first line of a <path.tex> document
 \documentclass[10pt, letterpaper, twoside]{article}
@@
 \postdate{\end{flushleft}}
+
+% edit the following line to "fix" the data
 \date{\today}
+
 % edit the following line for the title of the article
 \title{article title}
+
 % edit the following line for the author(s) of the article
 \author{article author}
+
 \setlength{\parindent}{0pt}
@@
 % very useful for hyperlinks
+\usepackage[unicode]{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    urlcolor=magenta,
+    citecolor=green
+}
+
+% required for bibtex URLs
+\usepackage{url}
+
 % useful for Greek letters in text mode
@@
 \usepackage[style=authoryear]{biblatex}
-\addbibresource{pilon_gilles.bib}
+\addbibresource{~/documents/repositories/latex/pilon_gilles_bibliography.bib}
+
+% useful for the glossary
+\usepackage[toc, acronym, nopostdot, numberedsection, record=hybrid, shortcuts=ac, abbreviations]{glossaries-extra}
+\makeglossaries
+\GlsXtrLoadResources[
+    src={pilon_gilles_glossary.bib},
+    selection={recorded and deps},
+    sort=letter-nocase
+]
 
 % define theorem-like elements
-\theoremstyle{myenv}
-\theoremstyle{mytheorem}
+% \theoremstyle{myenv}
+% \theoremstyle{mytheorem}
 \newtheorem{theorem}{Theorem}
@@
 \newtheorem{axiom}[theorem]{Axiom}
-\theoremstyle{mydefinition}
+% \theoremstyle{mydefinition}
 \newtheorem{definition}[theorem]{Definition}
@@
 
-\usepackage[unicode]{hyperref}
-\hypersetup{
-    colorlinks=true,
-    urlcolor=magenta,
-    citecolor=green,
-    linkcolor=red
-}
-
 % this is the end of the preamble section
@@
 \maketitle
+
+\renewcommand{\epigraphflush}{flushleft}
+\renewcommand{\textflush}{flushleft}
+\renewcommand{\sourceflush}{flushleft}
+\epigraph{A picture is worth a thousand words.}{Anon}
+
+\begin{figure}[H]
+\includegraphics[scale=0.25, left]{../fot/matplotlib_anatomy_of_a_figure.png}
+\caption{Anatomy of a matplotlib figure}
+\end{figure}
 
@@
 \section{Introduction}\label{sec:introduction}
-\renewcommand{\epigraphflush}{flushleft}
-\renewcommand{\textflush}{flushleft}
-\renewcommand{\sourceflush}{flushleft}
-\epigraph{Remember, the objective is to take the right action on the process. No
-credit is given for finding the `right numbers.'}{Donald J. Wheeler}
-
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 
-\subsection{Simple table}\label{sec:simple_table}`
+\subsection{Simple table}\label{sec:simple_table}
 
@@
 
-\subsection{Multirow table}\label{sec:multirow_table}`
+\subsection{Multirow table}\label{sec:multirow_table}
 \begin{table}[H]
@@
 
-\subsection{Inline mathematics}\label{sec:inline_mathematics}`
+\subsection{Inline mathematics}\label{sec:inline_mathematics}
 Examples of inline mathematics $\frac{a}{b}$, followed by text and another inline equation $\lim_{x\to 0}\frac{\sin x}{x}$=1 and more text $\sum_{k=0}^\infty \frac{1}{2^k}=2$ and finally much more text to cover many lines of a paragraph.
@@
 \newpage
+\section{Glossary terms}\label{sec:glossary_terms}
+
+Here is a request to fill in \gls{dependent_variable} and \glspl{dependent_variable}.
+
+For dual abbreviations and glossary terms, \gls{anome}.
+
+\newpage
 \listoffigures
@@
 
-\newpage
-\listofmylemmas
+% \newpage
+% \listofmylemmas
 
-\newpage
-\listofmypropositions
+% \newpage
+% \listofmypropositions
 
@@
 Add files, data, and other supporting information, and where it can be obtained.
+all
+
+\newpage
+\printunsrtglossary[type={abbreviations}]
+
+\newpage
+\printunsrtglossary[style={indexgroup}]
 

### 2022-08-09 article.tex
Moved "list of" to after table of contents
Refactor location of lists, remove several newpage

@@
 \newpage
+\listoffigures
+
+\listoftables
+
+\listofmyequations
+
+\listofmytheorems
+
+\listofmydefinitions
+
+\listofmycorollaries
+
+\newpage
 \section{Introduction}\label{sec:introduction}
@@
 
-\newpage
-\section{Bold, italics, and underline}\label{sec:bold_italics_underline}
+\section{Creating bold, italics, and underline}\label{sec:bold_italics_underline}
 Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.
 
-\section{URLs}\label{sec:urls}
+\section{Creating URLs}\label{sec:urls}
 Hyperlinks within the document can be easily added.
@@
 Hyperlinks to external URLs can be easily added. For example, see \href{https://en.wikipedia.org/wiki/Latex}{Wikipedia \LaTeX}.
-\section{Lists}\label{sec:lists}
+
+\newpage
+\section{Creating lists}\label{sec:lists}
 \subsection{Unordered list}\label{sec:unordered_list}
@@
 \newpage
-\section{Graphics}\label{sec:graphics}
+\section{Inserting graphics}\label{sec:graphics}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 \newpage
-\section{Tables}\label{sec:tables}
+\section{Creating tables}\label{sec:tables}
 
@@
 \newpage
-\section{Mathematics}\label{sec:mathematics}
+\section{Creating mathematics}\label{sec:mathematics}
 
@@
 \newpage
-\section{Greek letters}\label{sec:greek_letters}
+\section{Creating greek letters}\label{sec:greek_letters}
 
@@
 \newpage
-\section{Theorems}\label{sec:theorems}
+\section{Creating theorems}\label{sec:theorems}
 
@@
 
-\section{Definitions}\label{sec:definitions}
+\section{Creating definitions}\label{sec:definitions}
 
@@
 
-\section{Corollaries}\label{sec:corollaries}
+\section{Creating corollaries}\label{sec:corollaries}
 \begin{corollary}
@@
 
-\newpage
-\section{Lemmas}\label{sec:lemmas}
+\section{Creating lemmas}\label{sec:lemmas}
 \begin{lemma}
@@
 
-\begin{lemma}
-$q=r$
-\end{lemma}
-\mylemmas{Lem 3}
-
-\begin{lemma}
-$x+y=z$
-\end{lemma}
-\mylemmas{Lem 4}
-
-\begin{lemma}
-$z-r+t=3$
-\end{lemma}
-\mylemmas{Lem 5}
-
-\begin{lemma}
-$q=r$
-\end{lemma}
-\mylemmas{Lem 6}
-
-\newpage
-\section{Propositions}\label{sec:propositions}
+\section{Creating propositions}\label{sec:propositions}
 \begin{proposition}
@@
 \newpage
-\section{Citations}\label{sec:citations}
+\section{Inserting citations}\label{sec:citations}
 
@@
 
-\newpage
-\section{Glossary terms}\label{sec:glossary_terms}
+\section{Inserting glossary terms}\label{sec:glossary_terms}
 
@@
 For dual abbreviations and glossary terms, \gls{anome}.
-
-\newpage
-\listoffigures
-
-\newpage
-\listoftables
-
-\newpage
-\listofmyequations
-
-\newpage
-\listofmytheorems
-
-\newpage
-\listofmydefinitions
-
-\newpage
-\listofmycorollaries
 

### 2022-08-25 article.tex
Refactor sections for clarity
Fix equation numbering

@@
 \newpage
+\section*{Acknowledgements}\label{sec:acknowledgements}
+
+The author wishes to thank ...
+
+\section*{Supporting information}\label{sec:supporting_information}
+
+Add files, data, and other supporting information, and where it can be obtained.
+
 \listoffigures
@@
 \begin{flalign}
-    \text{distance to nearest specification} & = \frac{\text{nearest specification} - \text{location statistic}}{\text{dispersion statistic}}&& \\
-                                             & = \frac{\text{min}\,(\overline{X} - \text{LSL}\,, \text{USL} - \overline{X})}{s}&&
+    \text{distance to nearest spec} = \frac{\text{nearest spec} - \text{location statistic}}{\text{dispersion statistic}}  = \frac{\text{min}\,(\overline{X} - \text{LSL}\,, \text{USL} - \overline{X})}{s} &&
 \end{flalign}
@@
 \end{flalign}
+\myequations{Matrix p format}
 
@@
 \end{flalign}
+\myequations{Matrix b format}
 
@@
 
-Here is a request to fill in \gls{dependent_variable} and \glspl{dependent_variable}.
+Here is a request to fill in \gls{dependentvariable} and \glspl{dependentvariable}.
 
 For dual abbreviations and glossary terms, \gls{anome}.
+
+\gls{fixedeffectsmodel}
+
+\gls{randomeffectsmodel}
+
+\gls{expectedmeansquares}
+
+\gls{mixedeffectsmodel}
 
@@
 % \listofmypropositions
-
-\newpage
-\section{Acknowledgements}\label{sec:acknowledgements}
-
-The author wishes to thank ...
-
-\section{Supporting information}\label{sec:supporting_information}
-
-Add files, data, and other supporting information, and where it can be obtained.
-all
 

### 2022-12-15 article.tex
Add blocking
Add items for display
Change variables names

@@
 
-Here is a request to fill in \gls{dependentvariable} and \glspl{dependentvariable}.
+Here is a request to fill in \gls{endog}, \glspl{endog}, \gls{exog}, and \glspl{exog}.
 
-For dual abbreviations and glossary terms, \gls{anome}.
+For dual abbreviations and glossary terms, \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, and \gls{anome}.
 
-\gls{fixedeffectsmodel}
-
-\gls{randomeffectsmodel}
-
-\gls{expectedmeansquares}
-
-\gls{mixedeffectsmodel}
+\gls{interaction}
 

### 2024-09-12 article.tex
Add fontenc for 8 bit fonts 256 glyphs
Edit comment re fontenc
Add glossary term machineleaning
Add gls terms
Edit content

@@
 
+% required for 8 bit fonts 256 glyphs
+\usepackage[T1]{fontenc}
+
 % useful for Greek letters in text mode
@@
 % useful for the glossary
-\usepackage[toc, acronym, nopostdot, numberedsection, record=hybrid, shortcuts=ac, abbreviations]{glossaries-extra}
+\usepackage[toc, nopostdot, numberedsection, record=hybrid, shortcuts=ac, abbreviations]{glossaries-extra}
 \makeglossaries
 \GlsXtrLoadResources[
-    src={pilon_gilles_glossary.bib},
+    src={~/documents/repositories/latex/pilon_gilles_glossary.bib},
     selection={recorded and deps},
-    sort=letter-nocase
+    sort=letter-nocase,
+    selection={all} % shows all glossary entries
 ]
@@
 
-The author wishes to thank ...
+The author wishes to thank ... \LaTeX and \LaTeXe
 
@@
 
-Here is a single citation with postnote only. $C_\text{pm}$ is a complex subject (\cite[][pages 1-10]{chan1988}).
+Here is a single citation with postnote only. $C_\text{pm}$ is a complex subject (\cite[][1-10]{chan1988}).
 
@@
 
-Here is a request to fill in \gls{endog}, \glspl{endog}, \gls{exog}, and \glspl{exog}.
+Here is a request to fill in \gls{endog}, \glspl{endog}, \gls{exog}, \glspl{exog}, \gls{machinelearning}, and \gls{seborrheickeratosis}.
 
-For dual abbreviations and glossary terms, \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, and \gls{anome}.
+For dual abbreviations and glossary terms, \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, \gls{anome}, \gls{iam}, \gls{pam}, \gls{edr}, \glsxtrlong{xdr}, \gls{pythonnamespace}, \gls{cybersecurity}.
 

### 2024-12-13 article.tex
Edit cotnent

@@
 
+% use this package for better control over quotes
+\usepackage{csquotes}
+
 % very useful for hyperlinks
@@
 }
+
+\usepackage{xcolor}
 
@@
 ]
+
+% the above shows every single term in pilon_gilles_glossary.bib
+% use the following instead when only list terms used in the document
+
+% \GlsXtrLoadResources[
+%     src={~/documents/repositories/latex/pilon_gilles_glossary.bib},
+%     selection={recorded and deps},
+%     sort=letter-nocase
+% ]
 
@@
 
-For dual abbreviations and glossary terms, \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, \gls{anome}, \gls{iam}, \gls{pam}, \gls{edr}, \glsxtrlong{xdr}, \gls{pythonnamespace}, \gls{cybersecurity}.
+For glossary terms use \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, \gls{anome}, \gls{iam}, \gls{pam}, \gls{edr}, \glsxtrlong{xdr}, \gls{pythonnamespace}, \gls{cybersecurity}.
 
@@
 
-\newpage
-\printunsrtglossary[type={abbreviations}]
+% \newpage
+% \printunsrtglossary[type={abbreviations}]
 

### 2025-06-13 curriculum_vitae.tex
Create curriculum_vitae.tex

\documentclass[10pt, letterpaper, twoside]{article} % Using article class for simplicity
\usepackage[utf8]{inputenc}     % For correct handling of special characters
\usepackage[sfdefault]{noto}
\usepackage[T1]{fontenc}        % For proper font encoding
\usepackage[nohyper]{ragged2e}  % For \RaggedRight to left-align content
\usepackage{geometry}           % For easy margin setting
\usepackage{url}                % For formatting URLs
\usepackage{titlesec}           % For controlling section spacing
\usepackage{enumitem}           % For controlling list indentation

% --- Custom Section Formatting ---
% \titleformat{<command>}[<shape>]{<format>}{<label>}{<sep>}{<before-code>}[<after-code>]
\titleformat{\section}[block]{\bfseries\large}{\thesection}{1em}{}

% --- Geometry Settings ---
\geometry{margin=0.5in} % Set all margins to 1 inch

% --- Page Style (No Page Numbers) ---
\pagestyle{empty}

% --- Reduce Section Spacing ---
% \titlespacing{<command>}{<left>}{<before-skip>}{<after-skip>}
\titlespacing{\section}{0pt}{12pt}{5pt}
\titlespacing{\subsection}{0pt}{8pt}{3pt}

% --- Custom Em Dash Macro (if you defined it) ---
\newcommand{\spacedemdash}{\,---\,} % Example: if you want thin spaces

% --- Global Itemize Indentation & Spacing Control (MODIFIED) ---
\setlist[itemize]{
    leftmargin=*,      % Keeps text flush with left margin
    topsep=0pt,        % Reduces space before the first item
    partopsep=0pt,     % Reduces additional space if list starts new paragraph
    itemsep=0pt,       % Reduces space between individual items
    parsep=0pt         % Reduces space between paragraphs *within* an item (if any)
}

% --- Discourage hyphenation
\hyphenpenalty=10000   % Discourage hyphenation of words
\exhyphenpenalty=10000 % Discourage hyphenation of words already containing hyphens

\begin{document}
% --- Apply \RaggedRight to the entire document body (excluding centered parts) ---
\RaggedRight

% --- Contact Information ---
\begin{center}
    \textbf{\large FIRSTNAME LASTNAME} \\
    city province \\
    telephone \\
    email \\
    \url{https://github.com/yourid} \\
    \url{https://www.linkedin.com/in/yourid/}
\end{center}

% --- Professional Title ---
% \RaggedRight ensures the content is left-aligned from here onwards.
% Place it before the content you want to affect.
% \centerline{\textbf{Senior Machine Learning Engineer}}

\section*{SUMMARY}
insert text

\section*{EXPERIENCE}

\noindent\textbf{company \textbar ~city province \textbar ~title} \hfill \textbf{yyyy-mm\spacedemdash yyyy-mm} \\
brief job description
\begin{itemize}
    \item achievement
    \item achievement
\end{itemize}
\vspace{8pt}

\noindent\textbf{company \textbar ~city province \textbar ~title} \hfill \textbf{yyyy-mm\spacedemdash yyyy-mm} \\
brief job description
\begin{itemize}
    \item achievement
    \item achievement
\end{itemize}
\vspace{8pt}

\section*{SKILLS}
skill, skill, ...

\section*{EDUCATION}
degree, major, university, city province

\end{document}
